### 2019-11-05 paper/02mprelim.tex

\section{Mathematical preliminaries}
\subsection{Boundary value problems}
Consider a polygonal domain $\Omega \subset \mathbb{R}^2$ with boundary $\Gamma.$ 
Let $\gamma:[0,L] \to \Gamma$ be an arclength parametrization, and $\nu(t)$ denote the 
outward-pointing normal to $\Gamma$ at $\gamma(t).$  
Let $\omega \in \mathbb{C}$ in the first quadrant of the complex plane denote the 
Helmholtz wave number.
For ease of exposition our primary focus in the first portion of this paper will be on the 
following four boundary value problems.
\begin{enumerate}
\item The interior Dirichlet problem:
\begin{align}\label{eqn:BVPID}
(\Delta + \omega^2)u(x) &= 0, \hspace{1 cm} x \in \Omega,\\
u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in [0,L].
\end{align}

\item The exterior Dirichlet problem:
\begin{align}\label{eqn:BCPED}
(\Delta + \omega^2) u(x) &= 0, \hspace{1 cm} x \in \mathbb{R}^2\setminus\Omega,\\
u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in[0,L].
\end{align}

\item The interior Neumann problem:
\begin{align}\label{eqn:BVPIN}
(\Delta + \omega^2) u(x) &= 0, \hspace{1 cm} x \in \Omega,\\
\nabla u(\gamma(t))\cdot \nu(t)  &= f(t), \hspace{0.45 cm} t\in [0,L].
\end{align}

\item The exterior Neumann problem:
\begin{align}\label{eqn:BVPEN}
(\Delta + \omega^2) u(x) &= 0, \hspace{1 cm} x \in \mathbb{R}^2\setminus\Omega,\\
\nabla u(\gamma(t))\cdot \nu(t)  &= f(t), \hspace{0.45 cm} t\in [0,L].
\end{align}

@@

\begin{remark}
The existence and uniqueness of solutions to the above equations is a classical result. 
The exterior Dirichlet problem and interior Neumann problem require the additional assumption that
$$\int_0^L f(t)\,{\rm d}t = 0.$$
\end{remark}

>>>>

\section{Mathematical preliminaries}
\subsection{Boundary value problems}
Consider a polygonal domain $\Omega \subset \mathbb{R}^2$ with boundary $\Gamma.$ 
Let $\gamma:[0,L] \to \Gamma$ be an arclength parametrization, and $\nu(t)$ denote the 
outward-pointing normal to $\Gamma$ at $\gamma(t).$  
Let $\omega \in \mathbb{C} \setminus \{ 0 \}$ in the first quadrant of the complex plane denote the 
Helmholtz wave number.
\begin{enumerate}
\item The interior Dirichlet problem for Laplace's equation:
\begin{align}\label{eqn:BVPIDL}
\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in [0,L].
\end{align}

\item The interior Dirichlet problem for Helmholtz's equation:
\begin{align}\label{eqn:BVPIDH}
(\Delta + \omega^2) u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in [0,L].
\end{align}

\item The exterior Dirichlet problem for Laplace's equation:
\begin{align}\label{eqn:BVPEDL}
\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \mathbb{R}^2\setminus\Omega,\\
u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in[0,L], \\
u(\bx) &= O(1) , \hspace{0.4cm} |\bx| \to \infty.
\end{align}

\item The exterior Dirichlet problem for Helmholtz's equation:
\begin{align}\label{eqn:BVPEDH}
\Delta u(\bx) &= 0, \hspace{1 cm} x \in \mathbb{R}^2\setminus\Omega,\\
u(\gamma(t)) &= f(t), \hspace{0.43 cm} t \in[0,L], \\
\sqrt{|\bx|} \left|\partial_{|\bx|} u - i\omega u(\bx)\right| &\to 0 , \hspace{0.86cm} |\bx| \to \infty.
\end{align}

\item The interior Neumann problem for Laplace's equation:
\begin{align}\label{eqn:BVPINL}
\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
\nabla u(\gamma(t))\cdot \bnu(t)  &= f(t), \hspace{0.45 cm} t\in [0,L],\\
\int_{0}^{L} f(t) dt &= 0.
\end{align}

\item The interior Neumann problem for Helmholtz's equation:
\begin{align}\label{eqn:BVPINH}
(\Delta + \omega^2) u(\bx) &= 0, \hspace{1 cm} \bx \in \Omega,\\
\nabla u(\gamma(t))\cdot \bnu(t)  &= f(t), \hspace{0.45 cm} t\in [0,L].
\end{align}

\item The exterior Neumann problem for Laplace's equation:
\begin{align}\label{eqn:BVPEDL}
\Delta u(\bx) &= 0, \hspace{1 cm} \bx \in \mathbb{R}^2\setminus\Omega,\\
\nabla u(\gamma(t))\cdot \bnu(t)  &= f(t), \hspace{0.43 cm} t \in[0,L], \\
\left|u(\bx) + \left(\frac{1}{2\pi} \int_{0}^{L} f(t) dt\right) \log{|\bx|}\right| &\to 0 , \hspace{0.4cm} |\bx| \to \infty.
\end{align}

\item The exterior Neumann problem for Helmholtz's equation:
\begin{align}\label{eqn:BVPEDH}
\Delta u(\bx) &= 0, \hspace{1 cm} x \in \mathbb{R}^2\setminus\Omega,\\
\nabla u(\gamma(t))\cdot \bnu(t)  &= f(t), \hspace{0.43 cm} t \in[0,L], \\
\sqrt{|\bx|} \left|\partial_{|\bx|} u - i\omega u(\bx)\right| &\to 0 , \hspace{0.86cm} |\bx| \to \infty.
\end{align}

@@

\begin{remark}
The existence and uniqueness of solutions to the above equations is a classical result. 
The interior Dirichlet and Neumann problems for Helmholtz equation have a countable set of
real $\omega$'s (which only accumulate at $\infty$)  for which the PDE has a non-unique solution. 
\end{remark}

### 2019-11-05 paper/03bvp.tex

 \section{Boundary integral equations}
A classical way of solving the interior and exterior Dirchlet and Neumann Laplace boundary value problems given above is to convert them to boundary integral equations. Before describing this reduction we first define the single and double layer potential operators and summarize their relevant properties.
 \subsection{Layer potentials}
\begin{definition}
Given a density $\sigma$ defined on $\Gamma$ the single-layer potential is defined by
\beqn
\cS[\sigma](\by) = -\frac{1}{2\pi} \int_{\Gamma} \log{|\bx - \by|} \sigma(\bx) dS_{\bx}.
\eeqn
Similarly, the double-layer potential is defined via the formula
\beqn
\cD[\sigma](\by) = \frac{1}{2\pi} \int_{\Gamma} \frac{\nu(\bx) \cdot( \by-\bx)}{|\bx-\by|^2}\sigma(\bx) dS_{\bx},
\eeqn
where with some abuse of notation we denote the normal to $\Gamma$ at $\bx$ by $\nu(\bx).$
\end{definition}
\begin{definition}
For $\bx \in \Gamma$ we define the kernel $K(x,y)$ by
\begin{equation}
K(\bx,\by) =\frac{1}{2\pi}  \frac{\nu(\bx) \cdot( \by-\bx)}{|\bx-\by|^2},
\end{equation}
where $\nu(\bx)$ is the normal to $\Gamma$ at $\bx.$ It is often convenient to work instead with the parametrization of $K$ which we will denote by $k:[0,L]\times k[0,L] \to \mathbb{R}$ and is defined by
\begin{align}
k(s,t) = \frac{1}{2 \pi} \frac{\nu(s) \cdot( \gamma(t)-\gamma(s))}{|\gamma(s)-\gamma(t)|^2}.
\end{align}
\end{definition}

@@

\begin{theorem}\label{thm:potlim}
Suppose the point $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the inside along a path such that 
\begin{align}
-1+\alpha<\frac{\bx-\bx_0}{\|\bx-\bx_0\|} \cdot \gamma'(t_0) <1-\alpha
\end{align}
for some $\alpha >0.$ Then 
\begin{align}
&\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
&\lim_{\bx \to \bx_0} \cD[\rho](\bx) = \cD[\rho](\bx_0)- \rho(\bx_0)\\
&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS\rho(\bx+\tau \nu(t_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx_0+\tau \nu(t_0))+ \rho(\bx_0).
\end{align}
Similarly, if $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the outside then
\begin{align}
&\lim_{\bx \to \bx_0} \cS[\sigma](\bx) = \cS[\sigma](\bx_0)\\
&\lim_{\bx \to \bx_0} \cD[\rho](\bx) = \cD[\rho](\bx_0)+ \rho(\bx_0)\\
&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx+\tau \nu(t_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS[\rho](\bx_0+\tau \nu(t_0))- \rho(\bx_0).
\end{align}
\end{theorem}

We define the following operator which arises in the study of Neumann boundary value problems.
\begin{definition}
Let $\cS$ be the single-layer potential operator. Let $\nu\cdot \nabla \cS$  denote its normal derivative restricted to $\Gamma.$ In particular, for $\by \in \Gamma,$
\begin{align}
\nu\cdot \nabla \cS[\rho] (\by) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau = 0} \cS[\rho](\by + \tau \nu(t_0)),
\end{align}
where $\gamma(t_0) = \by.$
\end{definition}

The following proposition relates the normal derivative of the single-layer operator to the double-layer operator. Its proof follows directly from the definitions.
\begin{proposition}
Let $\cS,\cD:L^2(\Gamma) \to L^2(\Gamma)$ be defined as above. Let $\nu \cdot \nabla \cS$ denote the normal derivative of $\cS$ in the sense of the previous definition. Then $\nu \cdot \nabla \cS = \cD^*$ where $*$ denotes the adjoint operator. In particular, for all $\rho,\sigma \in L^2(\Gamma)$
\begin{align}
\cD[\sigma](\gamma(t)] = \int_0^L k(s,t)\,\sigma(\gamma(s))\, {\rm d}s
\end{align}
and
\begin{align}
\nu\cdot \nabla\cS[\rho](\gamma(t)] = \int_0^L k(t,s)\,\rho(\gamma(s))\, {\rm d}s.
\end{align}
\end{proposition}

@@

\begin{theorem}
Let $\sigma \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
\begin{align}
f(s)= - \sigma(s)+ \int_0^L k(t,s)\,\sigma(t)\,{\rm d}t,
\label{bie_intd}
\end{align}
for all $s \in [0,L].$ For $f \in L^2([0,L])$ the above integral equation has a unique solution for $\sigma \in L^2([0.L]).$ Moreover, the solution to the interior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{theorem}
Let $\sigma \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
\begin{align}
f(s)=  \sigma(s)+ \int_0^L k(t,s)\,\sigma(t)\,{\rm d}t,
\end{align}
for all $s \in [0,L].$ For $f \in L^2([0,L])$ such that
\begin{align}
\int_0^L f(t)\,{\rm d}t = 0
\end{align}
 the above integral equation has a unique solution for $\sigma \in L^2([0.L]).$ Moreover, the solution to the exterior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD[\sigma](\by)$
for all $\by \in \mathbb{R}^2 \setminus \Omega.$
\end{theorem}

\begin{theorem}
Let $\rho \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
\begin{align}
f(s)= \rho(s)+ \int_0^L k(s,t)\,\rho(t)\,{\rm d}t,
\end{align}
for all $s \in [0,L].$ For $f \in L^2([0,L])$ the above integral equation has a unique solution for $\rho \in L^2([0,L])$  if and only if
\begin{align}
\int_0^L f(t)\,{\rm d}t.
\end{align}
 Moreover, the solution to the interior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\rho](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{theorem}
Let $\rho \in L^2([0,L])$ and $f: [0,L] \rightarrow \mathbb{R}$ be defined via the formula
\begin{align}
f(s)= -\rho(s)+ \int_0^L k(s,t)\,\rho(t)\,{\rm d}t,
\end{align}
for all $s \in [0,L].$ For $f \in L^2([0,L])$ the above integral equation has a unique solution for $\rho \in L^2([0.L]).$ Moreover, the solution to the exterior Neumann problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cS[\rho](\by)$ for all $\by \in \Omega.$
\end{theorem}

>>>>

 \section{Boundary integral equations}
A classical way of solving the interior and exterior Dirchlet and Neumann Laplace and Helmholtz boundary value problems given above is to convert them to boundary integral equations. Before describing this reduction we first define the single and double layer potential operators and summarize their relevant properties.
 \subsection{Layer potentials}
\begin{definition}
Given a density $\sigma$ defined on $\Gamma$ the single-layer potential is defined by
\beqn
\cS_{\omega}[\sigma](\by) =  \int_{\Gamma} G_{\omega} (\bx,\by)\sigma(\bx) dS_{\bx} \, ,
\eeqn
where
\beqn
G_{\omega}(\bx,\by) = \begin{cases} 
\frac{i}{4} H_{0}(\omega |\bx-\by|) &\quad \omega \neq 0 \,, \\
-\frac{1}{2\pi} \log{|\bx-\by|} &\quad \omega = 0.
\end{cases}
\eeqn
Here $H_{0}$ is the Hankel 
function of the first kind of order $0$. 
Similarly, the double-layer potential is defined via the formula
\beqn
\cD_{\omega}[\sigma](\by) =\int_{\Gamma} \bnu(\bx) \cdot \nabla_{\bx} G_{\omega}(\bx,\by) \sigma(\bx) dS_{\bx},
\eeqn
where with some abuse of notation we denote the normal to $\Gamma$ at $\bx$ by $\bnu(\bx).$
\end{definition}
\begin{remark}
The layer potentials $\cS_{0}[\sigma]$ and $\cD_{0}[\omega]$ are the layer potentials for Laplace's equation.
\end{remark}
\begin{definition}
For $\bx \in \Gamma$ we define the kernel $K_{\omega}(\bx,\by)$ by
\begin{equation}
K_{\omega}(\bx,\by) =\bnu(\bx) \cdot \nabla_{\bx} G_{\omega}(\bx,\by),
\end{equation}
where $\nu(\bx)$ is the normal to $\Gamma$ at $\bx.$ It is often convenient to work instead with the parametrization of $K_{\omega}$ which we will denote by $k_{\omega}:[0,L]\times k[0,L] \to \mathbb{R}$ and is defined by
\begin{align}
k_{\omega}(s,t) = K_{\omega}(\gamma(s),\gamma(t)).
\end{align}
\end{definition}

@@

\begin{theorem}\label{thm:potlim}
Suppose the point $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the inside along a path such that 
\begin{align}
-1+\alpha<\frac{\bx-\bx_0}{\|\bx-\bx_0\|} \cdot \gamma'(t_0) <1-\alpha
\end{align}
for some $\alpha >0.$ Then 
\begin{align}
&\lim_{\bx \to \bx_0} \cS_{\omega}[\sigma](\bx) = \cS_{\omega}[\sigma](\bx_0)\\
&\lim_{\bx \to \bx_0} \cD_{\omega}[\rho](\bx) = \cD_{\omega}[\rho](\bx_0)- \rho(\bx_0)\\
&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS_{\omega}[\rho](\bx+\tau \bnu(t_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS_{\omega}[\rho](\bx_0+\tau \bnu(t_0))+ \rho(\bx_0).
\end{align}
Similarly, if $\bx$ approaches a point $\bx_0 = \gamma(t_0)$ from the outside then
\begin{align}
&\lim_{\bx \to \bx_0} \cS_{\omega}[\sigma](\bx) = \cS_{\omega}[\sigma](\bx_0)\\
&\lim_{\bx \to \bx_0} \cD_{\omega}[\rho](\bx) = \cD_{\omega}[\rho](\bx_0)+ \rho(\bx_0)\\
&\lim_{\bx \to \bx_0} \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS_{\omega}[\rho](\bx+\tau \bnu(t_0)) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau= 0}\cS_{\omega}[\rho](\bx_0+\tau \bnu(t_0))- \rho(\bx_0).
\end{align}
\end{theorem}

We define the following operator which arises in the study of Neumann boundary value problems.
\begin{definition}
Let $\cS_{\omega}$ be the single-layer potential operator. Let $\bnu\cdot \nabla \cS_{\omega}$  denote its normal derivative restricted to $\Gamma.$ In particular, for $\by \in \Gamma,$
\begin{align}
\bnu(\by)\cdot \nabla \cS_{\omega}[\rho] (\by) = \left.\frac{{\rm d}}{{\rm d}\tau}\right|_{\tau = 0} \cS_{\omega}[\rho](\by + \tau \bnu(t_0)),
\end{align}
where $\gamma(t_0) = \by.$
\end{definition}

The following proposition relates the normal derivative of the single-layer operator to the double-layer operator. Its proof follows directly from the definitions.
\begin{proposition}
Let $\cS_{\omega},\cD_{\omega}:L^2(\Gamma) \to L^2(\Gamma)$ be defined as above. Let $\bnu \cdot \nabla \cS_{\omega}$ denote the normal derivative of $\cS_{\omega}$ in the sense of the previous definition. Then $\bnu \cdot \nabla \cS _{\omega}= \cD_{\omega}^{T}$ where $T$ denotes the adjoint operator with respect to the inner product
\beqn
< f,g > = \int_{0}^{L} f(\gamma(t)) g(\gamma(t)) dt\,.
\eeqn
In particular, for all $\rho,\sigma \in L^2(\Gamma)$
\begin{align}
\cD_{\omega}[\sigma](\gamma(t)] = \int_0^L k_{\omega}(s,t)\,\sigma(\gamma(s))\, {\rm d}s
\end{align}
and
\begin{align}
\bnu(\gamma(t))\cdot \nabla\cS_{\omega}[\rho](\gamma(t)] = \int_0^L k_{\omega}(t,s)\,\rho(\gamma(s))\, {\rm d}s.
\end{align}
\end{proposition}

@@

\begin{theorem} [Interior Dirichlet problem for the Laplace and Helmholtz equations]
Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$. If $\omega$ is not an Dirichlet resonance of $\Omega$, then 
there exists a unique $\sigma \in L^{2}[0,L]$ which satisfies
\begin{align}
f(s)= - \sigma(s)+ \int_0^L k_{\omega}(t,s)\,\sigma(t)\,{\rm d}t,
\label{bie_intd}
\end{align}
Moreover, the solution to the interior Dirichlet problem for Laplace/Helmeholtz equation with boundary data $f$ is given by $u(\by) = \cD_{\omega}[\sigma](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{theorem} [Exterior Dirichlet problem for the Laplace equation]
Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$. Then there exists a unique $\sigma \in L^{2}[0,L]$ which
satisfies
\begin{align}
f(s)=  \sigma(s)+ \int_0^L (k_{0}(t,s) + 1)\,\sigma(t)\,{\rm d}t,
\end{align}
for all $s \in [0,L].$ 
Moreover, the solution to the exterior Dirichlet problem for Laplace's equation with boundary data $f$ is given by $u(\by) = \cD_{0}[\sigma](\by) + \int_{0}^{L} \sigma(t) dt$
for all $\by \in \mathbb{R}^2 \setminus \Omega.$
\end{theorem}

\begin{theorem} [Exterior Dirichlet problem for the Helmholtz equation]
Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$. Suppose $\omega$ is not an interior Neumann resonance of $\Omega$. Then there exists a unique $\sigma \in L^{2}[0,L]$ which
satisfies
\begin{align}
f(s)=  \sigma(s)+ \int_0^L k_{\omega}(t,s) \,\sigma(t)\,{\rm d}t,
\end{align}
for all $s \in [0,L].$ 
Moreover, the solution to the exterior Dirichlet problem for Helmholtz's equation with boundary data $f$ is given by $u(\by) = \cD_{\omega}[\sigma](\by)$
for all $\by \in \mathbb{R}^2 \setminus \Omega.$
\end{theorem}

\begin{theorem}[Interior Neumann problem for the Laplace equation]
Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$ and satisfy $\int_{0}^{L} f(t) = 0$ \, .
Then there exists a unique $\rho \in L^{2}[0,L]$ which satisfies
\begin{align}
f(s)=  \rho(s)+ \int_0^L (k_{0}(s,t) + 1)\,\sigma(t)\,{\rm d}t,
\label{bie_intd}
\end{align}
Moreover, the solution to the interior Neumann problem for Laplace equation with boundary data $f$ is given by $u(\by) = \cS_{0}[\rho](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{theorem}[Interior Neumann problem for the Helmholtz equation]
Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$. Suppose that $\omega$ is not an interior Neumann resonance for 
$\Omega$. 
Then there exists a unique $\rho \in L^{2}[0,L]$ which satisfies
\begin{align}
f(s)=  \rho(s)+ \int_0^L k_{\omega}(s,t) \,\sigma(t)\,{\rm d}t,
\label{bie_intd}
\end{align}
Moreover, the solution to the interior Neumann problem for the Helmholtz equation with boundary data $f$ is given by $u(\by) = \cS_{\omega}[\rho](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{theorem}[Exterior Neumann problem for the Laplace and Helmholtz equations]
Let $f:[0,L] \rightarrow \mathbb{C}$ be in $L^{2}[0,L]$. Suppose that $\omega$ is not an interior Dirichlet resonance for 
$\Omega$. 
Then there exists a unique $\rho \in L^{2}[0,L]$ which satisfies
\begin{align}
f(s)=  \rho(s)+ \int_0^L k_{\omega}(s,t) \,\sigma(t)\,{\rm d}t,
\label{bie_intd}
\end{align}
Moreover, the solution to the interior Neumann problem for the Laplace ($\omega =0$) and Helmholtz equation with boundary data $f$ is given by $u(\by) = \cS_{\omega}[\rho](\by)$ for all $\by \in \Omega.$
\end{theorem}

\begin{remark}
Even though the exterior Dirichlet and Neumann problems for Helmholtz equations are well-posed partial differential equations, the corresponding integral equations obtained by setting $u = \cD_{\omega}[\sigma](\by)$ for the Dirichlet problem and
$u = \cS_{\omega}[\rho](\by)$ are known to have a countable set of spurious resonances at the interior Neumann and Dirichlet resonances respectively. These spurious resonances can be eliminated by using a combined field integral representation 
for $u$ instead. We defer the extension of our method to the combined field representation to section (ENTER section number here).
\end{remark}
